### 2019-05-07 paper/plots/lqg_mu/plot.tex
added tikz plots

\documentclass{standalone} 
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}

\usepackage{pgfplots}
\usepackage{pgfplotstable}

\usepgfplotslibrary{groupplots}
\usetikzlibrary{matrix}
\usepgfplotslibrary{fillbetween}
\usetikzlibrary{pgfplots.colorbrewer}
\usetikzlibrary{plotmarks}

\pgfplotsset{every tick label/.append style={font=\small\rmfamily}}
\pgfplotsset{every axis/.append style={font=\small\rmfamily, ylabel near ticks, xlabel near ticks}}

\pgfplotsset{
        % define a `cycle list' for marker
     	cycle list/.define={my marks}{
          solid, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=*\\
          densely dashed, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=triangle*\\
          densely dotted, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=square*\\
          densely dashdotted, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=diamond*\\
          densely dash dot dot, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=|\\
          solid, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=x\\
          %every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=star\\
        },
    }

\pgfplotstableread[col sep = comma]{./OPTIMIST.csv}\optimist
\pgfplotstableread[col sep = comma]{./GPUCB.csv}\gpucb
\pgfplotstableread[col sep = comma]{./UCB1.csv}\ucb

\renewcommand{\rmdefault}{ptm}
\newcommand{\mathbr}[1]{\bm{\mathbf{#1}}}

\newcommand\drawplot[5]{
	\addplot table[x=iteration, y={#2}]{#5};\label{plots:#1}
	\def\temp{#3}\ifx\temp\empty
	\else
		\addplot[name path=up, draw=none, forget plot] table[x=iteration, y={#3}]{#5};
    	\addplot[name path=low, draw=none, forget plot] table[x=iteration, y={#4}]{#5};
    	\addplot[/pgfplots/refstyle={plots:#1}, fill opacity=0.2, forget plot] fill between[of=up and low];
	\fi
	\addlegendentry{#1}
}

\begin{document}

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={10}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=6cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.48,0.95)},anchor=north east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

        			\drawplot{OPTIMIST}{mean}{up}{low}{\optimist}
        			\drawplot{UCB1}{mean}{up}{low}{\ucb}
        			\drawplot{GPUCB}{mean}{up}{low}{\gpucb}

			\end{groupplot}

\end{tikzpicture}

\end{document}

### 2019-05-07 paper/plots/mc/plot.tex
added tikz plots

--- 2019-05-07 paper/plots/lqg_mu/plot.tex
@@
 \pgfplotstableread[col sep = comma]{./OPTIMIST.csv}\optimist
-\pgfplotstableread[col sep = comma]{./GPUCB.csv}\gpucb
-\pgfplotstableread[col sep = comma]{./UCB1.csv}\ucb
+\pgfplotstableread[col sep = comma]{./PGPE.csv}\pgpe
+\pgfplotstableread[col sep = comma]{./PBPOIS.csv}\pbpois
 
@@
 
-\newcommand\drawplot[5]{
-	\addplot table[x=iteration, y={#2}]{#5};\label{plots:#1}
+\newcommand\drawplot[6]{
+	\def\todraw{#1}\ifx\todraw\empty
+		\addplot[draw=none] coordinates {(1,1)};
+	\else
+		\addplot table[x=iteration, y={#2}, each nth point={#6}]{#5};\label{plots:#1}
+		%\addlegendentry{#1}
 		\def\temp{#3}\ifx\temp\empty
@@
 		\fi
-	\addlegendentry{#1}
+	\fi
 }
@@
 
-\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={10}]
+\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
     		\begin{groupplot}[cycle list/Dark2-6,
@@
 							  },
-							  legend style={thin, draw=gray, at={(0.48,0.95)},anchor=north east},
+							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                       		  grid=both,
@@
         					   xlabel={Episodes},
-        					   ylabel={Cumulative Regret}]
+        					   ylabel={Cumulative Average Return}]
 
-        			\drawplot{OPTIMIST}{mean}{up}{low}{\optimist}
-        			\drawplot{UCB1}{mean}{up}{low}{\ucb}
-        			\drawplot{GPUCB}{mean}{up}{low}{\gpucb}
+        			\drawplot{OPTIMIST}{mean}{up}{low}{\optimist}{4}
+        			\drawplot{}{}{}{}{}{}
+        			\drawplot{}{}{}{}{}{}
+        			\drawplot{PGPE}{mean}{up}{low}{\pgpe}{1}
+        			\drawplot{PB-POIS}{mean}{up}{low}{\pbpois}{1}
+        			\legend{OPTIMIST,,,PGPE, PB-POIS};
 

### 2019-05-08 paper/plots/mc/plot.tex
added river swim experiment

@@
                 				very thick \nextlist},
-                      		  height=6cm,
+                      		  height=5cm,
                       		  width=7cm,  
-                      		  ylabel style={yshift=-0.1cm},
+                      		  %ylabel style={yshift=-0.1cm},
                       		  xlabel style={yshift=0.1cm},
@@
         					   xlabel={Episodes},
-        					   ylabel={Cumulative Average Return}]
+        					   ylabel={Cumulative Return}]
 

### 2019-05-08 paper/plots/riverswim/plot.tex
added river swim experiment

\documentclass{standalone} 
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}

\usepackage{pgfplots}
\usepackage{pgfplotstable}

\usepgfplotslibrary{groupplots}
\usetikzlibrary{matrix}
\usepgfplotslibrary{fillbetween}
\usetikzlibrary{pgfplots.colorbrewer}
\usetikzlibrary{plotmarks}

\pgfplotsset{every tick label/.append style={font=\small\rmfamily}}
\pgfplotsset{every axis/.append style={font=\small\rmfamily, ylabel near ticks, xlabel near ticks}}

\pgfplotsset{
        % define a `cycle list' for marker
     	cycle list/.define={my marks}{
          solid, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=*\\
          densely dashed, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=triangle*\\
          densely dotted, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=square*\\
          densely dashdotted, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=diamond*\\
          densely dash dot dot, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=|\\
          solid, every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=x\\
          %every mark/.append style={solid,fill=\pgfkeysvalueof{/pgfplots/mark list fill}},mark=star\\
        },
    }

\pgfplotstableread[col sep = comma]{./OPTIMIST_disc_20.csv}\optdisc
\pgfplotstableread[col sep = comma]{./OPTIMIST_disc_100.csv}\optdiscc
\pgfplotstableread[col sep = comma]{./OPTIMIST_cont_k2.csv}\optcontd
\pgfplotstableread[col sep = comma]{./OPTIMIST_cont_k3.csv}\optcontt
\pgfplotstableread[col sep = comma]{./OPTIMIST_cont_k4.csv}\optcontq
\pgfplotstableread[col sep = comma]{./PGPE.csv}\pgpe

\renewcommand{\rmdefault}{ptm}
\newcommand{\mathbr}[1]{\bm{\mathbf{#1}}}

\newcommand\drawplot[6]{
	\def\todraw{#1}\ifx\todraw\empty
		\addplot[draw=none] coordinates {(1,1)};
	\else
		\addplot table[x=iteration, y={#2}, each nth point={#6}]{#5};\label{plots:#1}
		%\addlegendentry{#1}
		\def\temp{#3}\ifx\temp\empty
		\else
			\addplot[name path=up, draw=none, forget plot, each nth point={#6}] table[x=iteration, y={#3}]{#5};
    		\addplot[name path=low, draw=none, forget plot, each nth point={#6}] table[x=iteration, y={#4}]{#5};
    		\addplot[/pgfplots/refstyle={plots:#1}, fill opacity=0.2, forget plot, each nth point={#6}] fill between[of=up and low];
		\fi
	\fi
}

\begin{document}

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 2 by 2},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
%        		\nextgroupplot[title={}, 
%        					   xlabel={Episodes},
%        					   ylabel={Cumulative Average Return}]
%        			
%        			\drawplot{OPTIMIST discrete 20}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdisc}{4}
%        			\drawplot{OPTIMIST discrete 100}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdiscc}{4}
%        			\drawplot{OPTIMIST2 ($k=2$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontd}{4}
%        			\drawplot{OPTIMIST2 ($k=3$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontt}{4}
%        			\drawplot{OPTIMIST2 ($k=4$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontq}{4}
%        			\drawplot{PGPE}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\pgpe}{1}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

        			\drawplot{OPTIMIST discrete 20}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontq}{4}
        			\drawplot{PGPE}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\pgpe}{1}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Per-Step Regret}]

        			\drawplot{OPTIMIST discrete 20}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontq}{4}
        			\drawplot{PGPE}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\pgpe}{1}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Probability Right action}]

        			\drawplot{OPTIMIST discrete 20}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontq}{4}

        	\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Grid Size}]

        			\drawplot{OPTIMIST discrete 20}{GridSize_mean}{GridSize_up}{GridSize_low}{\optdisc}{4}
        			\drawplot{OPTIMIST discrete 100}{GridSize_mean}{GridSize_up}{GridSize_low}{\optdiscc}{4}
        			\drawplot{OPTIMIST2 ($k=2$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontd}{4}
        			\drawplot{OPTIMIST2 ($k=3$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontt}{4}
        			\drawplot{OPTIMIST2 ($k=4$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontq}{4}

			\end{groupplot}

			\path (myplot c1r1.south west|-current bounding box.south)--
      			coordinate(legendpos)
      			(myplot c2r1.south east|-current bounding box.south);
			\matrix[matrix of nodes,
    				anchor=north,
    				inner sep=0.4em,
    				draw=none,
    				font=\rmfamily%\scriptsize\rmfamily
  					]at([yshift=0ex]legendpos)
  					{ 	
						\ref{plots:OPTIMIST discrete 20}& OPTIMIST (20 arms)&
    					\ref{plots:OPTIMIST discrete 100}& OPTIMIST (100 arms)&
    					\ref{plots:OPTIMIST2 ($k=2$)}& OPTIMIST2 ($\kappa=2$)\\
    					\ref{plots:OPTIMIST2 ($k=3$)}& OPTIMIST2 ($\kappa=3$)&	
    					\ref{plots:OPTIMIST2 ($k=4$)}& OPTIMIST2 ($\kappa=4$)&	
    					\ref{plots:PGPE}& PGPE\\	
    					};

\end{tikzpicture}

\end{document}

### 2019-05-08 paper/plots/riverswim/plot_main.tex
added river swim experiment

--- 2019-05-08 paper/plots/riverswim/plot.tex
@@
 \usepackage{bm}
+\usepackage{amsmath}
 
@@
                       		  horizontal sep=2cm,
-                      		  group size= 2 by 2},
+                      		  group size= 1 by 1},
             				mark list fill={.!75!white},
@@
                       		  width=7cm,  
-                      		  ylabel style={yshift=-0.1cm},
+                      		  %ylabel style={yshift=-0.1cm},
                       		  xlabel style={yshift=0.1cm},
@@
 							  },
-							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
+							  xtick={0,1000,2000,3000,4000,5000},
+							  legend style={thin, draw=gray, at={(0.95,0.32)},anchor=south east},
                       		  grid=both,
@@
                       		  ]
-%        		\nextgroupplot[title={}, 
-%        					   xlabel={Episodes},
-%        					   ylabel={Cumulative Average Return}]
-%        			
-%        			\drawplot{OPTIMIST discrete 20}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdisc}{4}
-%        			\drawplot{OPTIMIST discrete 100}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdiscc}{4}
-%        			\drawplot{OPTIMIST2 ($k=2$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontd}{4}
-%        			\drawplot{OPTIMIST2 ($k=3$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontt}{4}
-%        			\drawplot{OPTIMIST2 ($k=4$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontq}{4}
-%        			\drawplot{PGPE}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\pgpe}{1}
-
         		\nextgroupplot[title={}, 
         					   xlabel={Episodes},
-        					   ylabel={Cumulative Regret}]
+        					   ylabel={Cumulative Return}]
 
-        			\drawplot{OPTIMIST discrete 20}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optdisc}{4}
-        			\drawplot{OPTIMIST discrete 100}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optdiscc}{4}
-        			\drawplot{OPTIMIST2 ($k=2$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontd}{4}
-        			\drawplot{OPTIMIST2 ($k=3$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontt}{4}
-        			\drawplot{OPTIMIST2 ($k=4$)}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\optcontq}{4}
-        			\drawplot{PGPE}{CumRegret_mean}{CumRegret_up}{CumRegret_low}{\pgpe}{1}
-
-        	\nextgroupplot[title={}, 
-        					   xlabel={Episodes},
-        					   ylabel={Per-Step Regret}]
-
-        			\drawplot{OPTIMIST discrete 20}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optdisc}{4}
-        			\drawplot{OPTIMIST discrete 100}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optdiscc}{4}
-        			\drawplot{OPTIMIST2 ($k=2$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontd}{4}
-        			\drawplot{OPTIMIST2 ($k=3$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontt}{4}
-        			\drawplot{OPTIMIST2 ($k=4$)}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\optcontq}{4}
-        			\drawplot{PGPE}{PerStepRegret_mean}{PerStepRegret_up}{PerStepRegret_low}{\pgpe}{1}
-
-        	\nextgroupplot[title={}, 
-        					   xlabel={Episodes},
-        					   ylabel={Probability Right action}]
-
-        			\drawplot{OPTIMIST discrete 20}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optdisc}{4}
-        			\drawplot{OPTIMIST discrete 100}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optdiscc}{4}
-        			\drawplot{OPTIMIST2 ($k=2$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontd}{4}
-        			\drawplot{OPTIMIST2 ($k=3$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontt}{4}
-        			\drawplot{OPTIMIST2 ($k=4$)}{RiverSwim_mu1_actor_mean}{RiverSwim_mu1_actor_up}{RiverSwim_mu1_actor_low}{\optcontq}{4}
-
-        	\nextgroupplot[title={}, 
-        					   xlabel={Episodes},
-        					   ylabel={Grid Size}]
-
-        			\drawplot{OPTIMIST discrete 20}{GridSize_mean}{GridSize_up}{GridSize_low}{\optdisc}{4}
-        			\drawplot{OPTIMIST discrete 100}{GridSize_mean}{GridSize_up}{GridSize_low}{\optdiscc}{4}
-        			\drawplot{OPTIMIST2 ($k=2$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontd}{4}
-        			\drawplot{OPTIMIST2 ($k=3$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontt}{4}
-        			\drawplot{OPTIMIST2 ($k=4$)}{GridSize_mean}{GridSize_up}{GridSize_low}{\optcontq}{4}
+        			\drawplot{OPTIMIST discrete 20}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optdisc}{4}
+        			\drawplot{OPTIMIST2 ($k=2$)}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\optcontd}{4}
+        			\drawplot{}{}{}{}{}{}
+        			\drawplot{PGPE}{ReturnMean_mean}{ReturnMean_up}{ReturnMean_low}{\pgpe}{1}
+        			\legend{OPTIMIST (20 arms),OPTIMIST2 ($\kappa=2$),,PGPE};
 
 			\end{groupplot}
-
-			\path (myplot c1r1.south west|-current bounding box.south)--
-      			coordinate(legendpos)
-      			(myplot c2r1.south east|-current bounding box.south);
-			\matrix[matrix of nodes,
-    				anchor=north,
-    				inner sep=0.4em,
-    				draw=none,
-    				font=\rmfamily%\scriptsize\rmfamily
-  					]at([yshift=0ex]legendpos)
-  					{ 	
-						\ref{plots:OPTIMIST discrete 20}& OPTIMIST (20 arms)&
-    					\ref{plots:OPTIMIST discrete 100}& OPTIMIST (100 arms)&
-    					\ref{plots:OPTIMIST2 ($k=2$)}& OPTIMIST2 ($\kappa=2$)\\
-    					\ref{plots:OPTIMIST2 ($k=3$)}& OPTIMIST2 ($\kappa=3$)&	
-    					\ref{plots:OPTIMIST2 ($k=4$)}& OPTIMIST2 ($\kappa=4$)&	
-    					\ref{plots:PGPE}& PGPE\\	
-    					};
 

### 2019-05-29 talk/animation/spaces1.tex
draft with animations

\documentclass[tikz,border=3.14pt]{standalone}
\usepackage{../mymacros}
\usepackage{tikz-3dplot}
\begin{document}
\begin{tikzpicture}[]
\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
\phantom{
\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta}$};
\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
\draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
\draw[] (-1.1,-5,0) node (c) {$R(\tau)$};
\draw[->] (b) -- (c);
}
\end{tikzpicture}
\end{document}

### 2019-05-29 talk/animation/spaces6.tex
draft with animations

--- 2019-05-29 talk/animation/spaces1.tex
@@
 \draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
+\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_1$};
+\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_1$};
 \phantom{
-\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
@@
 \draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
-\draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
-\draw[] (-1.1,-5,0) node (c) {$R(\tau)$};
-\draw[->] (b) -- (c);
+\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta)$};
+\draw[->, dashed, color=blue!60!white] (-0.7,-3.5,0) -- (c);
 }
+\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_1)$};
+\draw[->, dashed, color=blue!60!white] (a) -- (c);
+\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_2)$};
+\draw[->, dashed, color=red!60!white] (b) -- (d);
+\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};
 \end{tikzpicture}

### 2019-05-29 talk/animation/spaces8.tex
draft with animations

\documentclass[tikz,border=3.14pt]{standalone}
\usepackage{../mymacros}
\usepackage{tikz-3dplot}
\usetikzlibrary{fadings}

\tikzfading[name=fade out,
inner color=transparent!0, outer color=transparent!100]

\begin{document}
\begin{tikzpicture}[]
\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (0.5 and .2) node[above, shift={(-.1,.1)}, color=blue!60!white]{$p_{\vtheta_1}$};

\draw[fill,color=red!60!white, path fading = fade out, draw=none] (-0.5,-3.7,0) ellipse (0.5 and .2);
\draw[color=red!60!white] (-0.8,-3.8,0) node{$p_{\vtheta_2}$};

\draw[fill,color=green!60!white, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
\draw[color=green!60!white] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};

\draw[fill,color=black!60!white, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
\draw[color=black!60!white] (1.2,-3.4,0) node{$p_{\vtheta}$};

\end{tikzpicture}
\end{document}

### 2019-05-29 talk/animation/spaces9.tex
draft with animations

--- 2019-05-29 talk/animation/spaces8.tex
@@
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (0.5 and .2) node[above, shift={(-.1,.1)}, color=blue!60!white]{$p_{\vtheta_1}$};
-
-\draw[fill,color=red!60!white, path fading = fade out, draw=none] (-0.5,-3.7,0) ellipse (0.5 and .2);
-\draw[color=red!60!white] (-0.8,-3.8,0) node{$p_{\vtheta_2}$};
-
-\draw[fill,color=green!60!white, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
-\draw[color=green!60!white] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};
+\draw[fill,color=violet!60!white, path fading = fade out, draw=none] (-0.5,-3.5,0) ellipse (.8 and .4);
+\draw[color=violet!60!white] (-0.9,-3.2,0) node{$\Phi_t$};
 

### 2019-05-30 talk/animation/spaces10.tex
completed animations
fixed jumping frames

--- 2019-05-29 talk/animation/spaces6.tex
@@
 \begin{tikzpicture}[]
-\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
-\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_1$};
-\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_1$};
+\phantom{\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};}
+\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
+\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};
 \phantom{
@@
 \draw[->, dashed, color=blue!60!white] (-0.7,-3.5,0) -- (c);
-}
 \draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_1)$};
@@
 \draw[->, dashed, color=red!60!white] (b) -- (d);
-\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};
+\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};}
 \end{tikzpicture}

### 2019-05-30 talk/animation/spaces11.tex
completed animations
fixed jumping frames

--- 2019-05-29 talk/animation/spaces6.tex
@@
 \begin{tikzpicture}[]
-\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
-\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_1$};
-\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_1$};
+\phantom{\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};}
+\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
+\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};
 \phantom{
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta}$};
+\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta_A}$};
 \draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
-\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta)$};
+\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
 \draw[->, dashed, color=blue!60!white] (-0.7,-3.5,0) -- (c);
 }
-\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_1)$};
+\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
 \draw[->, dashed, color=blue!60!white] (a) -- (c);
-\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_2)$};
+\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
 \draw[->, dashed, color=red!60!white] (b) -- (d);

### 2019-05-30 talk/animation/spaces3.tex
draft with animations
fixed jumping frames

--- 2019-05-29 talk/animation/spaces1.tex
@@
 \usepackage{tikz-3dplot}
+\usetikzlibrary{fadings}
+
 \begin{document}
 \begin{tikzpicture}[]
+\draw[dashed, color=blue!60!white, opacity=0.3] (-0.7,-0.3,0) -- (-1.93,-3.5,0);
+\draw[dashed, color=blue!60!white, opacity=0.3] (-0.7,-0.3,0) -- (0.5,-3.5,0);
 \draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
-\phantom{
 \draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta}$};
-\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
+\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(.5,.25)}, color=blue!60!white]{$p_{\vtheta}$};
+
+\phantom{
 \draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
@@
 }
+\phantom{\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta)$};}
 \end{tikzpicture}

### 2019-05-30 talk/animation/spaces4.tex
draft with animations
fixed jumping frames

--- 2019-05-29 talk/animation/spaces1.tex
@@
 \usepackage{tikz-3dplot}
+\usetikzlibrary{fadings}
 \begin{document}
 \begin{tikzpicture}[]
+\draw[dashed, color=blue!60!white, opacity=0.3] (-0.7,-0.3,0) -- (-1.93,-3.5,0);
+\draw[dashed, color=blue!60!white, opacity=0.3] (-0.7,-0.3,0) -- (0.5,-3.5,0);
 \draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
-\phantom{
 \draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta}$};
-\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
+\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(.5,.25)}, color=blue!60!white]{$p_{\vtheta}$};
+%\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
 \draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
@@
 \draw[->] (b) -- (c);
-}
+\phantom{\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta)$};}
 \end{tikzpicture}

### 2019-05-30 talk/animation/spaces6.tex
fixed jumping frames

@@
 \draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
-\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_1$};
-\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_1$};
+\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
+\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};
 \phantom{
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta}$};
+\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta_A}$};
 \draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
-\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta)$};
+\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
 \draw[->, dashed, color=blue!60!white] (-0.7,-3.5,0) -- (c);
 }
-\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_1)$};
+\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
 \draw[->, dashed, color=blue!60!white] (a) -- (c);
-\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_2)$};
+\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
 \draw[->, dashed, color=red!60!white] (b) -- (d);

### 2019-05-31 poster/hist_swimmer.tex
updated slides; poster skeleton

\documentclass{standalone}
  \usepackage{pgfplots}
  \usepackage{amsmath}
  %\pgfplotsset{compat=1.12}
  \definecolor{greencol}{rgb}{0, 0.6, 0}
  \usepgfplotslibrary{fillbetween}

\pgfplotsset{every tick label/.append style={font=\scriptsize\rmfamily}}
\pgfplotsset{every axis/.append style={font=\scriptsize\rmfamily, ylabel near ticks, xlabel near ticks}}
\pgfplotsset{x axis/.append style={font=\textbf\scriptsize\rmfamily, xlabel near ticks}}
\usepgfplotslibrary{groupplots}
\usetikzlibrary{matrix}

\pgfplotsset{try min ticks=5}

  \begin{document}

      \begin{tikzpicture}
      \begin{axis}[
      grid=both,
grid style={gray!10},
      %legend pos=outer north east,
      %legend style={font=\tiny},
      %axis x line*=bottom,
      %axis y line*=left,
      %ylabel near ticks,
      %xlabel near ticks,     
      every tick/.style={gray!60},
      ylabel={\%},
      height=5cm,
      width=8cm,  
      ylabel style={yshift=-0.15cm},
      %xlabel style={yshift=-0.15cm},
      tick scale binop=\times,
      /pgf/number format/1000 sep={},
      xticklabel style={
        /pgf/number format/fixed,
        /pgf/number format/precision=5
	},
	 every x tick scale label/.style={
             at={(xticklabel* cs:0.92,0.1cm)},
             anchor=near xticklabel
         },
         symbolic x coords={Cartpole, Inverted Double Pendulum, Swimmer},
         xticklabels={\textbf{Cartpole}, $\footnotesize \substack{\text{\textbf{Inverted Double}} \\ \text{\textbf{ Pendulum}}}$, \textbf{Swimmer}},
         ybar=3pt,%ybar=2*\pgflinewidth,
         bar width=10pt,
%      width  = 0.50*\textwidth,
%      height = 8cm,
      major x tick style = transparent,
%      ybar=2*\pgflinewidth,
%      bar width=25pt,
      ymajorgrids = true,
%      
      xtick = data,
      scaled y ticks = false,
      enlarge x limits=0.2,
      ymin=0,
      legend cell align=left,
      legend style={at={(0.5,-0.2)},anchor=north},
      legend style={draw=none, legend columns=-1, column sep=1ex}
  ]

  	\addplot[blue, line width=0.3mm, style={fill=blue!50},error bars/.cd, y dir=both, y explicit,error bar style=blue]
           coordinates {
           (Cartpole, 99.44) += (0,0.27) -= (0,0.27)
           (Inverted Double Pendulum,95.95) += (0,4.3) -= (0,4.3)
           (Swimmer,92.4) += (0,0.57) -= (0,0.57)};

      \addplot[red, line width=0.3mm, style={fill=red!50},error bars/.cd, y dir=both, y explicit,error bar style=red]
          coordinates {
          (Cartpole, 90.94) += (0,2.8) -= (0,2.8)
          (Inverted Double Pendulum,71.6) += (0,4.29) -= (0,4.29)
          (Swimmer,80) += (0,1.7) -= (0,1.7)};

       \addplot[greencol, line width=0.3mm, style={fill=greencol!50},error bars/.cd, y dir=both, y explicit,error bar style={greencol}]
           coordinates {
           (Cartpole,100) += (0,0.77) -= (0,0.77)
           (Inverted Double Pendulum,100) += (0,1.1) -= (0,1.1)
           (Swimmer,100) += (0,0.21) -= (0,0.21)};

      \legend{A-POIS, P-POIS, TRPO}
  \end{axis}
  \end{tikzpicture}
  \end{document}

### 2019-05-31 talk/animation/spaces12.tex
updated slides; poster skeleton

\documentclass[tikz,border=3.14pt]{standalone}
\usepackage{../mymacros}
\usepackage{tikz-3dplot}
\usetikzlibrary{fadings}

\tikzfading[name=fade out,
inner color=transparent!0, outer color=transparent!100]

\begin{document}
\begin{tikzpicture}[]
\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};

\draw[dashed, color=blue!60!white, opacity=0.3] (-1.93,-3.5,0) -- (-0.7,-4.75,0);
\draw[dashed, color=blue!60!white, opacity=0.3] (0.5,-3.5,0) -- (-0.7,-4.75,0);
\draw[dashed, color=red!60!white, opacity=0.3] (-0.33,-3.5,0) -- (0.9,-4.75,0);
\draw[dashed, color=red!60!white, opacity=0.3] (2.1,-3.5,0) -- (0.9,-4.75,0);

\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(-.5,.2)}, color=blue!60!white]{$p_{\vtheta_A}$};
%\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
%\draw[->, dashed, color=blue!60!white] (-0.7,-3.5,0) -- (c);

\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
\draw[fill, color=red!60!white, path fading=fade out, draw=none] (0.9,-3.5,0) ellipse (1.25 and .4);
\draw[color=red!60!white] (1.4,-3.05,0) node{$p_{\vtheta_B}$};
%\draw[dashed, color=red!60!white] (b) -- (0.9,-3.5,0);
\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
%\draw[->, dashed, color=red!60!white] (0.9,-3.5,0) -- (d);

\draw[dashed, color=blue!60!white, opacity=0.3] (-0.7,-0.3,0) -- (-1.93,-3.5,0);
\draw[dashed, color=blue!60!white, opacity=0.3] (-0.7,-0.3,0) -- (0.5,-3.5,0);

\draw[dashed, color=red!60!white, opacity=0.3] (0.9,0.1,0) -- (-0.33,-3.5,0);
\draw[dashed, color=red!60!white, opacity=0.3] (0.9,0.1,0) -- (2.1,-3.5,0);

\draw[line width = 1.5pt, color=green!70!black,-latex] (-0.7,-3.4,0) arc[start angle=180,end angle=0, x radius = 0.8 cm , y radius =1 cm] node[shift={(-0.75,1.2)}]{\bf IS};

%\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_1)$};
%\draw[->, dashed, color=blue!60!white] (a) -- (c);
%\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_2)$};
%\draw[->, dashed, color=red!60!white] (b) -- (d);
%\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, %color=white]{\bf\Large MAB};
\end{tikzpicture}
\end{document}

### 2019-05-31 talk/animation/spaces8.tex
updated slides; poster skeleton

@@
 \begin{tikzpicture}[]
-\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
+\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1.5,1)}]{$\mathcal{T}$};
 \draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (0.5 and .2) node[above, shift={(-.1,.1)}, color=blue!60!white]{$p_{\vtheta_1}$};
@@
 
-\draw[fill,color=green!60!white, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
-\draw[color=green!60!white] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};
+\draw[fill,color=orange!60!white, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
+\draw[color=orange!60!white] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};
 
@@
 
+\draw[line width = 1.5pt, color=green!70!black,-latex] (-0.4,-3.2,0) arc[start angle=180,end angle=0, x radius = 0.8 cm , y radius =1 cm] node[shift={(-0.75,1.2)}]{\bf MIS};
+
 \end{tikzpicture}

### 2019-06-05 poster/plots/lqg_mu/plot.tex
complete poster draft

--- 2019-05-07 paper/plots/lqg_mu/plot.tex
@@
                 				very thick \nextlist},
-                      		  height=6cm,
-                      		  width=7cm,  
-                      		  ylabel style={yshift=-0.1cm},
+                      		  height=5cm,
+                      		  width=10cm,  
+                      		  %ylabel style={yshift=-0.1cm},
                       		  xlabel style={yshift=0.1cm},
@@
 							  },
-							  legend style={thin, draw=gray, at={(0.48,0.95)},anchor=north east},
+							  legend style={thin, draw=gray, at={(0.47,0.98)},anchor=north east},
                       		  grid=both,

### 2019-06-05 poster/plots/lqg_mu_sigma/plot.tex
complete poster draft

--- 2019-06-05 poster/plots/lqg_mu/plot.tex
@@
                       		  height=5cm,
-                      		  width=10cm,  
-                      		  %ylabel style={yshift=-0.1cm},
+                      		  width=7cm,  
+                      		  ylabel style={yshift=-0.1cm},
                       		  xlabel style={yshift=0.1cm},

### 2019-06-05 poster/plots/mc/plot.tex
complete poster draft

--- 2019-05-08 paper/plots/mc/plot.tex
@@
                       		  height=5cm,
-                      		  width=7cm,  
+                      		  width=10cm,  
                       		  %ylabel style={yshift=-0.1cm},

### 2019-06-06 talk/animation/spaces11.tex
small (graphical) fixes to slides

@@
 \usepackage{tikz-3dplot}
+
+\definecolor{poliblue1}{RGB}{93,138,168} 
+\definecolor{poliblue2}{RGB}{41,76,113}
+\definecolor{poliblue3}{RGB}{25,43,67}
+\definecolor{orangep}{RGB}{251,146,116}
+\definecolor{redp}{RGB}{245,86,91}
+\definecolor{greenp}{RGB}{73,165,150}
+
 \begin{document}
@@
 \phantom{\draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};}
-\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
-\draw [fill, color=red!60!white] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};
+\draw [fill, color=poliblue1] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta_A$};
+\draw [fill, color=redp] (0.9,0.1,0) circle (1.5pt) node[above](b){$\vtheta_B$};
 \phantom{
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta_A}$};
-\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
-\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
-\draw[->, dashed, color=blue!60!white] (-0.7,-3.5,0) -- (c);
+\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=poliblue1]{$p_{\vtheta_A}$};
+\draw[dashed, color=poliblue1] (a) -- (-0.7,-3.5,0);
+\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
+\draw[->, dashed, color=poliblue1] (-0.7,-3.5,0) -- (c);
 }
-\draw[color=blue!60!white] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
-\draw[->, dashed, color=blue!60!white] (a) -- (c);
-\draw[color=red!60!white] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
-\draw[->, dashed, color=red!60!white] (b) -- (d);
+\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
+\draw[->, dashed, color=poliblue1] (a) -- (c);
+\draw[color=redp] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
+\draw[->, dashed, color=redp] (b) -- (d);
 \draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};

### 2019-06-06 talk/animation/spaces4.tex
small (graphical) fixes to slides

--- 2019-05-29 talk/animation/spaces1.tex
@@
 \usepackage{tikz-3dplot}
+\usetikzlibrary{fadings}
+
+\definecolor{poliblue1}{RGB}{93,138,168} 
+\definecolor{poliblue2}{RGB}{41,76,113}
+\definecolor{poliblue3}{RGB}{25,43,67}
+\definecolor{orangep}{RGB}{251,146,116}
+
 \begin{document}
 \begin{tikzpicture}[]
+\draw[dashed, color=poliblue1, opacity=0.3] (-0.7,-0.3,0) -- (-1.93,-3.5,0);
+\draw[dashed, color=poliblue1, opacity=0.3] (-0.7,-0.3,0) -- (0.5,-3.5,0);
 \draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
-\phantom{
-\draw [fill, color=blue!60!white] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
+\draw [fill, color=poliblue1] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=blue!60!white]{$p_{\vtheta}$};
-\draw[dashed, color=blue!60!white] (a) -- (-0.7,-3.5,0);
+\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(.5,.25)}, color=poliblue1]{$p_{\vtheta}$};
+%\draw[dashed, color=poliblue1] (a) -- (-0.7,-3.5,0);
 \draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
@@
 \draw[->] (b) -- (c);
-}
+\phantom{\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta)$};}
 \end{tikzpicture}

### 2019-06-06 talk/animation/spaces8.tex
small (graphical) fixes to slides

--- 2019-05-29 talk/animation/spaces8.tex
@@
 
+\definecolor{poliblue1}{RGB}{93,138,168} 
+\definecolor{poliblue2}{RGB}{41,76,113}
+\definecolor{poliblue3}{RGB}{25,43,67}
+\definecolor{orangep}{RGB}{251,146,116}
+\definecolor{redp}{RGB}{245,86,91}
+\definecolor{greenp}{RGB}{73,165,150}
+\definecolor{waterp}{RGB}{134,195,180}
+
 \begin{document}
 \begin{tikzpicture}[]
-\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=blue!60!white, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (0.5 and .2) node[above, shift={(-.1,.1)}, color=blue!60!white]{$p_{\vtheta_1}$};
+\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1.5,1)}]{$\mathcal{T}$};
+\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (0.5 and .2) node[above, shift={(-.1,.1)}, color=poliblue1]{$p_{\vtheta_1}$};
 
-\draw[fill,color=red!60!white, path fading = fade out, draw=none] (-0.5,-3.7,0) ellipse (0.5 and .2);
-\draw[color=red!60!white] (-0.8,-3.8,0) node{$p_{\vtheta_2}$};
+\draw[fill,color=redp, path fading = fade out, draw=none] (-0.5,-3.7,0) ellipse (0.5 and .2);
+\draw[color=redp] (-0.8,-3.8,0) node{$p_{\vtheta_2}$};
 
-\draw[fill,color=green!60!white, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
-\draw[color=green!60!white] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};
+\draw[fill,color=orangep, path fading = fade out, draw=none] (-0.2,-3.5,0) ellipse (0.5 and .2);
+\draw[color=orangep] (0.1,-3.2,0) node{$p_{\vtheta_{t-1}}$};
 
-\draw[fill,color=black!60!white, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
-\draw[color=black!60!white] (1.2,-3.4,0) node{$p_{\vtheta}$};
+\draw[fill,color=waterp!80!black, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
+\draw[waterp!80!black] (1.2,-3.4,0) node{$p_{\vtheta}$};
+
+\draw[line width = 1.5pt, color=greenp,-latex] (-0.4,-3.2,0) arc[start angle=180,end angle=0, x radius = 0.8 cm , y radius =1 cm] node[shift={(-0.75,1.2)}]{\bf MIS};
 

### 2019-06-06 talk/animation/spaces9.tex
updated slides; poster skeleton
small (graphical) fixes to slides

@@
 
+\definecolor{poliblue1}{RGB}{93,138,168} 
+\definecolor{poliblue2}{RGB}{41,76,113}
+\definecolor{poliblue3}{RGB}{25,43,67}
+\definecolor{orangep}{RGB}{251,146,116}
+\definecolor{redp}{RGB}{245,86,91}
+\definecolor{greenp}{RGB}{73,165,150}
+\definecolor{violetp}{RGB}{215,113,161}
+\definecolor{waterp}{RGB}{134,195,180}
+
 \begin{document}
 \begin{tikzpicture}[]
-\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill,color=violet!60!white, path fading = fade out, draw=none] (-0.5,-3.5,0) ellipse (.8 and .4);
-\draw[color=violet!60!white] (-0.9,-3.2,0) node{$\Phi_t$};
+\draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1.5,1)}]{$\mathcal{T}$};
+\draw[fill,color=violetp, path fading = fade out, draw=none] (-0.5,-3.5,0) ellipse (.8 and .4);
+\draw[color=violetp] (-0.9,-3.2,0) node{$\Phi_t$};
 
-\draw[fill,color=black!60!white, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
-\draw[color=black!60!white] (1.2,-3.4,0) node{$p_{\vtheta}$};
+\draw[fill,color=waterp!80!black, path fading = fade out, draw=none] (1.,-3.7,0) ellipse (1 and .3);
+\draw[color=waterp!80!black] (1.2,-3.4,0) node{$p_{\vtheta}$};
+
+\draw[line width = 1.5pt, color=orangep,latex-latex] (-0.5,-3.5,0) --  (1.,-3.7,0) node[shift={(-0.75,0.5)}]{$d_2$};
 

### 2019-09-12 maple_talk/animation/spaces10.tex
very high level draft of longer talk for MAPLE 2019

--- 2019-06-06 talk/animation/spaces11.tex
@@
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=poliblue1]{$p_{\vtheta_A}$};
+\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=poliblue1]{$p_{\vtheta}$};
 \draw[dashed, color=poliblue1] (a) -- (-0.7,-3.5,0);
-\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
+\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta)$};
 \draw[->, dashed, color=poliblue1] (-0.7,-3.5,0) -- (c);
-}
-\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta_A)$};
+\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta_1)$};
 \draw[->, dashed, color=poliblue1] (a) -- (c);
-\draw[color=redp] (0.9,-5,0) node (d) {$J(\vtheta_B)$};
+\draw[color=redp] (0.9,-5,0) node (d) {$J(\vtheta_2)$};
 \draw[->, dashed, color=redp] (b) -- (d);
-\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};
+\draw[fill=black] (-1.5,-1.5,0) rectangle (1.7,-3.5,0) node[pos=.5, color=white]{\bf\Large MAB};}
 \end{tikzpicture}

### 2019-09-12 maple_talk/animation/spaces2.tex
very high level draft of longer talk for MAPLE 2019

--- 2019-06-06 talk/animation/spaces4.tex
@@
 \usepackage{tikz-3dplot}
-\usetikzlibrary{fadings}
 
@@
 \begin{tikzpicture}[]
-\draw[dashed, color=poliblue1, opacity=0.3] (-0.7,-0.3,0) -- (-1.93,-3.5,0);
-\draw[dashed, color=poliblue1, opacity=0.3] (-0.7,-0.3,0) -- (0.5,-3.5,0);
 \draw[] (0,0,0) ellipse (2 and .75) node[right, shift={(1,1)}]{$\Theta$};
 \draw [fill, color=poliblue1] (-0.7,-0.3,0) circle (1.5pt) node[above](a){$\vtheta$};
+\phantom{
 \draw[] (0,-3.5,0) ellipse (2.5 and .75) node[right, shift={(1,1)}]{$\mathcal{T}$};
-\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(.5,.25)}, color=poliblue1]{$p_{\vtheta}$};
-%\draw[dashed, color=poliblue1] (a) -- (-0.7,-3.5,0);
+\draw[fill, inner color=poliblue1, outer color=white, draw=none, color=white] (-0.7,-3.5,0) ellipse (1.25 and .4) node[above, shift={(1,.2)}, color=poliblue1]{$p_{\vtheta}$};
+\draw[dashed, color=poliblue1] (a) -- (-0.7,-3.5,0);
 \draw [fill, color=black] (-1.1,-3.6,0) circle (1.5pt) node[above](b){$\tau$};
@@
 \draw[->] (b) -- (c);
+}
 \phantom{\draw[color=poliblue1] (-0.7,-5,0) node (c) {$J(\vtheta)$};}
